\begin{longtable}{p{0.20\textwidth}@{\hspace{20pt}}p{0.59\textwidth}r}
\caption{Taxonomy clusters grouped by bias family with mechanistic descriptions}\label{tab:s6-taxonomy}\\
\toprule
Taxonomy cluster & Mechanistic description & $n_{\mathrm{biases}}$ \\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textbf{Table \thetable\ (continued)}}\\
\multicolumn{3}{@{}p{\textwidth}@{}}{Taxonomy clusters grouped by bias family with mechanistic descriptions}\\
\toprule
Taxonomy cluster & Mechanistic description & $n_{\mathrm{biases}}$ \\
\midrule
\endhead
\midrule
\multicolumn{3}{r}{\textit{Continued on next page}}\\
\endfoot
\bottomrule
\endlastfoot
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Attention \& Salience} ($n_{\mathrm{clusters}}=3$, $n_{\mathrm{biases}}=20$)} \\
Attentional Selection Under Load & Selective allocation of cognitive resources under high cognitive load distorts threat detection. & 8 \\
Salience Prominence And Vividness & Vivid, novel, or prominent stimuli capture attention disproportionate to their evidential value. & 6 \\
Threat And Warning Signal Processing & Repeated or irrelevant warning signals cause desensitization and habituation failures. & 6 \\
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Trust \& Credibility} ($n_{\mathrm{clusters}}=3$, $n_{\mathrm{biases}}=14$)} \\
Familiarity Fluency And Repetition & Repeated or fluently processed cues are misconstrued as indicators of trustworthiness. & 7 \\
First Impression And Surface Inference & Superficial surface features (e.g., logos, formatting) dominate credibility assessments. & 2 \\
Source Credibility Shortcuts & Peripheral source cues (authority, expertise signals) substitute for message-content evaluation. & 5 \\
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Evidence \& Belief} ($n_{\mathrm{clusters}}=5$, $n_{\mathrm{biases}}=38$)} \\
Anchoring And Framing & Initial numeric or categorical anchors disproportionately constrain subsequent estimates. & 6 \\
Causal Pattern And Story Completion & Narrative coherence drives premature causal closure, suppressing alternative hypotheses. & 8 \\
Confirmatory Processing & Prior beliefs selectively guide information search and weighting toward consistent evidence. & 8 \\
Representativeness And Diagnosticity Errors & Category membership is judged by surface similarity rather than base-rate probability. & 9 \\
Updating Failures & New evidence is underweighted relative to prior beliefs during sequential belief revision. & 7 \\
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Memory \& Source} ($n_{\mathrm{clusters}}=3$, $n_{\mathrm{biases}}=14$)} \\
Availability And Retrievability & Ease of memory retrieval is treated as a proxy for objective frequency or risk probability. & 3 \\
Reconstructive Memory Distortions & Memories are reconstructed using current knowledge, distorting recollection of past states. & 5 \\
Source Monitoring And Attribution Errors & The origin of information is misattributed, enabling successful spoofing and impersonation. & 6 \\
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Risk \& Probability} ($n_{\mathrm{clusters}}=4$, $n_{\mathrm{biases}}=24$)} \\
Certainty Ambiguity And Probability Weighting & Overweighting of certain and extreme-probability outcomes distorts expected-value reasoning. & 9 \\
Randomness Frequency And Small Sample Inference & Misperception of randomness and small-sample statistics biases threat prevalence estimates. & 3 \\
Reference Dependence And Risk Attitude & Outcomes are evaluated relative to a reference point, inducing asymmetric risk attitudes. & 6 \\
Vulnerability And Severity Estimation & Personal risk is underestimated due to optimism bias and unrealistic comparative assessments. & 6 \\
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Temporal \& Commitment} ($n_{\mathrm{clusters}}=4$, $n_{\mathrm{biases}}=17$)} \\
Control And Protective Action & Illusions of control lead to underinvestment in genuine risk-mitigation behaviors. & 3 \\
Escalation And Commitment & Sunk-cost reasoning perpetuates failing courses of action despite accumulating negative signals. & 5 \\
Inertia Delay And Nonaction & Status quo bias and procrastination prevent timely security-relevant behavioral responses. & 4 \\
Present Oriented Choice & Hyperbolic discounting of future risks reduces motivation for prospective security investment. & 5 \\
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Social \& Authority} ($n_{\mathrm{clusters}}=5$, $n_{\mathrm{biases}}=24$)} \\
Authority Deference And Compliance & Compliance with authority figures overrides independent evaluation of request legitimacy. & 3 \\
Conformity And Consensus & Social proof signals trigger norm-following behavior, enabling herd-exploitation attacks. & 6 \\
Group Identity And Intergroup Judgment & In-group favoritism and out-group derogation distort source credibility and trust allocation. & 7 \\
Liking Similarity Reciprocity And Scarcity & Persuasion principles (liking, reciprocity, scarcity) bypass deliberate evaluation of requests. & 4 \\
Responsibility Distribution And Public Self & Diffusion of responsibility reduces individual security behavior in shared system environments. & 4 \\
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Self-Assessment} ($n_{\mathrm{clusters}}=5$, $n_{\mathrm{biases}}=22$)} \\
Attribution Biases & Systematic attribution errors (self-serving, fundamental) distort causal accounts of security incidents. & 5 \\
Confidence Calibration Errors & Overconfidence in own security knowledge produces inadequate verification and oversight behavior. & 6 \\
Explanatory Forecasting And Projection Illusions & Hindsight and planning fallacies inflate subjective certainty about past and future security events. & 4 \\
Moral Self Regulation Distortions & Moral licensing and disengagement rationalize security policy violations as ethically acceptable. & 2 \\
Reflective Blind Spots And Closure & Bias blind spots and premature closure prevent self-corrective monitoring of own decision processes. & 5 \\
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Interface \& Automation} ($n_{\mathrm{clusters}}=3$, $n_{\mathrm{biases}}=14$)} \\
Automation And Algorithm Reliance & Over-reliance on automated systems reduces vigilance and critical verification of system outputs. & 5 \\
Option Structure And Order Effects & Default settings and option ordering disproportionately determine user security choices. & 6 \\
Routine Interaction And Alert Response & Habituated routines and alert fatigue suppress detection of anomalous or malicious events. & 3 \\
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Privacy \& Disclosure} ($n_{\mathrm{clusters}}=2$, $n_{\mathrm{biases}}=6$)} \\
Privacy And Disclosure Tradeoffs & Immediate convenience benefits are systematically overweighted against delayed privacy costs. & 2 \\
Self Presentation Visibility And Audience Misperception & Misjudgment of audience size and context leads to unintended information disclosure. & 4 \\
\addlinespace[2pt]\multicolumn{3}{@{}l}{\textbf{Affect \& Mood} ($n_{\mathrm{clusters}}=3$, $n_{\mathrm{biases}}=7$)} \\
Hot Cold Gaps And State Projection & Current emotional state is projected onto predicted future preferences, distorting risk planning. & 2 \\
Incidental Affect And Valuation & Task-irrelevant emotional states contaminate evaluations of unrelated security-relevant stimuli. & 2 \\
Mood Congruence And State Dependence & Memory retrieval and judgment are biased toward mood-congruent information. & 3 \\
\end{longtable}
